How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community

### 2018-11-02 Manuscript_draft/Manuscript_draft.Rmd
some changes

In natural systems plant species normally coexist and share their floral visitors with other species (Bascompte et al., 2003). This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs). Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss.

@@

The effect of heterospecific pollen has been widely studied (refs). Native species are supposed to have greater negative effects than native ones @arceo2016. However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008. Moreover, closely related species are supposed to reduce fitness in greter effect but the evidence is scarce and based on independent studies with different methodlogies (refs) or studies that just check that with very highly close related species with the aim of study hybridization (refs).

@@

Relatedness. What we know?

@@

@@

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10). The proxy of effect were seed set and "pollen tubes". Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10). Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).

>>>>

In natural systems plant species normally coexist and share their floral visitors with other species (Bascompte et al., 2003). This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs). Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss (Morales & Traveset 2008)

@@

The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008). Native species are supposed to have greater negative effect than native ones @arceo2016. However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008. Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs). There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect. Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect. Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.

@@

@@

Brown and Mitchell 2001 could be a good paper to explain why we pick seed set as a proxy and not fruit set. We cannot see changes on it, losing information with it.

@@

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10). Seed set was the proxy of effect (see Brown and Mitchell 2001, for differences in effect between seed set and fruit set) and "pollen tubes". Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10). Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).

### 2018-11-02 Manuscript_draft/Manuscript_draft.tex
some changes

In natural systems plant species normally coexist and share their floral
visitors with other species (Bascompte et al., 2003). This pollinator
sharing from the plant perpective can be negative due to competition
(refs) or positive due to facilitation (refs). Moreover, once the
pollinator has landed on the stigma some other issues for the species
fitness may arise, the arrival of foreign pollen and conspecific pollen
loss.

@@

The effect of heterospecific pollen has been widely studied (refs).
Native species are supposed to have greater negative effects than native
ones Arceo-Gómez and Ashman (2016)

species-specific. What kind of pollen interaction? Size just mechanical?

@@

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10). The proxy of effect were seed set
and ``pollen tubes''. Moreover, hand cross pollination, hand self
pollination, apomixis (bagged emasculated flowers) and natural selfing
were tested (N=10). Flowers were emasculated the day prior anthesis and
hand pollinated next day with a toothpick. Had-pollination was realized
with 3-4 gentle touches on the surface of the stigma. The mixes of
pollen were performed on an eppendorf based on the pollen counts maded
with Neubaeur chamber (each anther was counted 4 times for 20 different
anthers per species).

@@

>>>>

In natural systems plant species normally coexist and share their floral
visitors with other species (Bascompte et al., 2003). This pollinator
sharing from the plant perpective can be negative due to competition
(refs) or positive due to facilitation (refs). Moreover, once the
pollinator has landed on the stigma some other issues for the species
fitness may arise, the arrival of foreign pollen and conspecific pollen
loss (Morales \& Traveset 2008)

@@

The effect of heterospecific pollen has been widely studied (Morales \&
Traveset 2008). Native species are supposed to have greater negative
effect than native ones Arceo-Gómez and Ashman (2016). However, the
quantity of pollen that integrates in the network can be quite low
Bartomeus et al. (2008). Moreover, closely related species are supposed
to reduce fitness in greater effect but the evidence is scarce and based
on independent studies with different methodologies (Arceo-gomez \&
Ashman 2016) or studies that just check it with a pair of species that
are highly related with the aim to understand hybridization costs
(refs). There is a need to deepen into how relatednes is involve in the
costs of heterospecific pollen effect. Furthermore, following the
conceptual trait framework of Ashman and Arceo-Gomez on heterospecific
pollen there are good theoretical basis for trait effect.
Notwithstanding, non empirical work has tested how really these traits
are involved in heterospecific pollen effect.

@@

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10). Seed set was the proxy of effect
(see Brown and Mitchell 2001, for differences in effect between seed set
and fruit set) and ``pollen tubes''. Moreover, hand cross pollination,
hand self pollination, apomixis (bagged emasculated flowers) and natural
selfing were tested (N=10). Flowers were emasculated the day prior
anthesis and hand pollinated next day with a toothpick. Had-pollination
was realized with 3-4 gentle touches on the surface of the stigma. The
mixes of pollen were performed on an eppendorf based on the pollen
counts maded with Neubaeur chamber (each anther was counted 4 times for
20 different anthers per species).

@@

\hypertarget{ref-bartomeus2008}{}
Bartomeus, I., J. Bosch, and M. Vilà. 2008. High invasive pollen
transfer, yet low deposition on native stigmas in a carpobrotus-invaded
community. Annals of Botany 102:417--424.
